A Systematic Review of the Use of the ESM Methodology in Education

### 2020-08-05 paper_draft.Rmd
clean up document
update

This study  is a systematic review of studies in education that used the experience sampling method to collect data.

The experience sampling method (ESM) is a longitudinal data collection method that involves gathering data frequently from participants over an extended period of time. The use of ESM in education research is on the rise in recent years because it provides a unique way to collect data closer in time to students’ experiences that are of interest to researchers, and so this method provides a unique measure of ecological validity

>>>>

This studyis a systematic review of studies that used the experience sampling method to collect data in education settings.
checking push
The experience sampling method (ESM) is a longitudinal data collection method that involves gathering data frequently from participants over an extended period of time. The use of ESM in education research is on the rise in recent years because it provides a unique way to collect data closer in time to students’ experiences that are of interest to researchers, and so this method provides a unique measure of ecological validity
